\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,vmargin={2cm,2.2cm}, hmargin={1.5cm}]{geometry}

%\pagestyle{empty}
\begin{document}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}%A sequence of nine symbols (try it and see!)

\begin{center}
\Huge
\textbf{The Foxy ``Lathund''\\ for MacOS X \& Linux\footnote[2]{To a lesser extent.}}\\
\normalsize
\vspace{0.5cm}
\emph{By Mikael Lund and Bj\"orn Persson.
Last updated \today}
\end{center}

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Graphics}
\subsection{Convert vector graphics to bitmap with defined size and resolution}
This is useful for Word documents where correct graphic dimensions/resolution should be maintained \emph{before} importing. A hassle, but here's one way of doing it:
\begin{enumerate}
\item Open vector graphics in Preview.app
\item Create a new paper size in the desired format.
\item Print to PDF, selecting the new paper format.
\item Open new PDF in Gimp. You will be prompted for a resolution (DPI).
\item Save bitmap file to png, tiff etc.
\end{enumerate}
This could likely be done easier using ImageMagick's \verb"convert" command.

\subsection{Making vector illustrations}
Vector illustrations can be made in a number of different programs such as
\verb+Pages+, \verb+Keynote+, \verb+Powerpoint+ etc. To export them to a PDF file do as follows:
\begin{enumerate}
\item Create illustration and select the objects you wish to export.
\item Select \verb+Edit->Copy+
\item Launch Preview.app and select \verb+File->New From Clipboard+.
\item Export to PDF or any other format.
\end{enumerate}

\subsection{Conversion commands etc.}
\begin{table}[h!]
\center
\begin{tabular}{ll}\hline\hline
Action              & Command \\\hline
Crop PDF borders & \verb"pdfcrop file.pdf" \\
Convert PDF/EPS to 300 dpi tiff & \verb"convert -compress lzw -density 300x300 in.pdf out.tif" \\
Convert Xmgrace plot to pdf     & \verb"xmgrace -hardcopy -hdevice PDF file.agr"\\
Convert to monochrome           & \verb"convert -threshold 38% -despeckle out.jpg -monochrome in.jpg"\\
Print syntax-highlighted source code & \verb"enscript --media=a4 -E sourcefile"\\\hline
\end{tabular}\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Networking}
\subsection{Access scientific journals from home}
Establish an encrypted SSH-tunnel to any computer situated on campus:
\begin{enumerate}
\item From home: \verb+$ ssh -D 9999 username@host.at.campus+
\item In \verb+System Preferences->Network->Advanced->Proxies+ set SOCKS proxy to \verb+localhost+, port 9999.
\end{enumerate}
All your web browsing will now appear as if you are situated inside campus. If you have a slow connection, you may want to add ``-C'' in the ssh command to enable compression.  When you close the ssh connection you must again remove the proxy setting in the network preferences to return to ``normal'' browsing.

\subsection{Mount remote disks from SSH-servers}
For this \verb+sshfs+ needs to be installed -- for example using MacPorts or MacFUSE. In this example we will mount /disk/gloabal/mikael from the host milleotto,\\

\verb+$ sshfs milleotto.lunarc.lu.se:/disk/global/mikael mntdir+\\

\noindent The remote disk will appear in ``mntdir'' and you'll have full read and write access. To unmount, simply do ``\verb+umount mntdir+''. As usual ``-C'' will enable compression.

\subsection{Printing}
\subsubsection{Automatic CUPS detection}
For some reason, CUPS printer detection has been disable in some versions of MacOS (10.5, higher?). Use the following command to re-enable automatic discovery:\\

\verb+cupsctl BrowseRemoteProtocols=cups+

\subsubsection{Connect to a specific CUPS server}
If auto-detection fails, try adding ``ServerName SERVER'' to /etc/cups/client.conf. Note that this usually causes printing to hang if the computer is disconnected from the network and, hence not recommended for laptops.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Software}
\subsection{Port Managers}
...are handy interfaces to automatically download and install a large number of open source software. Usually they require that Xcode -- Apple's developer and compiler tools -- are installed.
\subsubsection{Macports}
\begin{table}[h!]
\center
\begin{tabular}{ll}\hline\hline
Command              & Action \\\hline
\verb"port search keyword" & search for a package\\
\verb+port variants packagename+ & show \emph{variants} of a package.\\
\verb"sudo port install packagename" & install a package.\\
\verb"sudo port install emacs +x11" & install emacs variant with X11 support.\\
\verb"sudo port -d selfupdate" & update entire package system (do this only occasionally)\\\hline
\end{tabular}\end{table}
%
Useful packages are \verb+grace gnuplot povray sshfs vim aspell wget gawk tetex findutils+

\subsubsection{Fink}
\begin{table}[h!]
\center
\begin{tabular}{ll}\hline\hline
Action              & Command \\\hline
Search for package  & \verb"apt-cache search package"\\
Install package     & \verb"sudo apt-get install package"\\
Update packages     &  \verb"sudo apt-get update|upgrade"\\
Install source fink package & \verb"sudo fink install package"\\\hline
\end{tabular}\end{table}

\subsection{Visual Molecular Dynamics}
Or just VMD is a very impressive program for molecular visualization/analysis and although the name refers to MD, it works nicely with MC. A speciel feature of the mac port is that the command line tool is buried. Here are two ways to surface it:
\begin{itemize}
\item[\$] \verb+ alias vmd='/Applications/VMD\ 1.8.6.app/Contents/vmd/vmd_MACOSXX86'+
\item[\$] \verb+ sudo ln -s /Applications/VMD\ 1.8.6.app/Contents/vmd/vmd_MACOSXX86 /usr/local/bin/vmd+\end{itemize}

\subsection{Faunus}
To fetch the newest revision from the subversion repository, do\\

\verb+$ svn checkout http://faunus.svn.sourceforge.net/svnroot/faunus/trunk faunus+\\

\noindent Make sure to specify the compiler in the Makefile -- in particular parallel execution works, as of now, much better on Intels C++ compiler than with g++.

\subsection{Prehistoric ACE/gr or ``Xmgr''}
Yikes! This is a hassle to compile on recent versions of MacOS, maybe because development has been frozen for a decade! Someone should give it another go with gfortran or similar. I have a PowerPC version running (compiled via Fink) on an Intel mac -- works nicely via the transparent rosetta emulation. Detailed instructions to follow.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Table of useful commands}
\begin{table}[h]
\begin{small}
\begin{tabular}{ll}\hline\hline
Action              & Command \\\hline
Pause/resume job    & \verb"kill -s STOP|CONT pid" \\
Suicide!            & \verb"kill -9 -1"\\
Launch logout-safe job  & \verb"nohup utility &" \\
\\
Drive information   & \verb"df -h"\\
Find file           & \verb'find * -iname "file*"'\\
Find large files    & \verb'find * -size +1000k printf "%p %k \n"'\\
Open file (mac)     & \verb"open file"\\
Mount disk image    & \verb"hdid image.dmg"\\
\\
Create zip archive  & \verb"zip -r zipfile.zip file(s)"\\
Test zip archive    & \verb"unzip -t zipfile.zip"\\
Unpack zip archive  & \verb"unzip zipfile.zip [file(s)]"\\
Create tar archive  & \verb"tar -czf archive.tar.gz directory"\\
List tar archive    & \verb"tar -tzf archive.tar.gz"\\
Unpack tar archive  & \verb"tar -xzf archive.tar.gz"\\
\\
System information  & \verb"cat /proc/cpuinfo" (linux) \\
                    & \verb"system_profiler" (mac) \\
\\
X11 focus           & \verb"defaults write com.apple.X11 wm_ffm -bool true"\\
Terminal.all focus  & \verb"defaults write com.apple.Terminal FocusFollowsMouse -string YES"\\
\\
Get svn repository   & \verb"svn checkout URL destdir"\\
Update to latest repository & \verb"svn update"\\
Review changes       & \verb"svn status" (go to top level dir to see all)\\
Compare with latest repository & \verb"svn status -u" (if astrisks, update)\\
Compare difference's after modification& \verb"svn diff"\\
Submit svn changes   & \verb"svn commit"\\
Add file or directory& \verb"svn add file"\\
Show log             & \verb"svn log"\\
Regret and undo modification & \verb"svn revert foo"\\
Remove conflict files        & \verb"svn resolved"(not need if using revert)\\
\hline
\end{tabular}
\end{small}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Specific to Theoretical Chemistry, Lund University}
\subsection{Home directories (most likely outdated?)}
User home directories are served via NFS by \verb'garm.teokem.lu.se'. Some
versions of Linux are not entirely compatible with MacOS which can cause
problems with file locking. This is used in \verb+Mail.app+, \verb+Address Book.app+
etc. and these programs will NOT work when home is on garm (as of
writing, Dec. 2006). To circumvent this \verb+~/Library+ can be placed on a
local disk and a symlink placed in the home directory (ln -s).
To setup MacOS for NFS to garm I suggest using the free program
\verb+NFS manager+ by Bresink.
There you will also find a nice manual on integrating MacOS in NFS
and NIS environments. When setup, the mount point can be checked in
\verb+NetInfo Manager+ and should have the following options: \verb+-s,-P,-b+.
A restart is most likely required for the changes to take effect.


\end{document}

